---
title: "Wells A11 and H12"
output: html_document
---


##Find the lowest and highest wells of each plate

```{r echo=FALSE, message=FALSE}

oldwd <- getwd()
if ( basename(oldwd) == "Reports" ) {
  setwd("..")
}


source("extreme-wells.R")

```


### Lowest wells

Plates binned by lowest well, ordered by well:
```{r echo=FALSE}
low_table
```


Lowest wells, ordered by column, then by row:
```{r echo=FALSE}
show( plot_extremes(low_table, order="bycol") )
```

Clearly wells A12, H12 and A2 stand out.

Lowest wells, ordered by row, then by column:
```{r echo=FALSE}
show( plot_extremes(low_table, order="byrow") )
```


Plates binned by lowest well, ordered by frequency (top 10 only):
```{r echo=FALSE}
head(arrange(low_table, desc(Freq)), n=10)
```


### Highest wells

Plates binned by highest well, ordered by well:
```{r echo=FALSE}
high_table
```

Highest wells, ordered by column, then by row:
```{r echo=FALSE}
show( plot_extremes(high_table, order="bycol") )
```


Highest wells, ordered by row, then by column:
```{r echo=FALSE}
show( plot_extremes(high_table, order="byrow") )
```


Plates binned by highest well, ordered by frequency (top 10 only):
```{r echo=FALSE}
head(arrange(high_table, desc(Freq)), n=10)
```

Looks like the bottom outside edge has many of the highest wells.


```{r echo=FALSE}
if ( basename(getwd()) == "Reports" ) {
  setwd(oldwd)
}

```
